First Exclusive Measurement of Deep Virtual Compton Scattering off $^4$He: Toward the 3D tomography of nuclei

### 2017-02-08 eg6-letters/coherent/dvcs_he4_prl.tex
nathan:  missed a bit in the last paragraph

%conclusion
In summary, we present the first exclusive measurement of coherent DVCS 
off $^4$He using the CLAS spectrometer supplemented  
by a specially designed RTPC. This dataset represents a 
unique source as the first exclusive coherent nuclear DVCS measurement which 
can be used to directly constrain GPD models. The measured beam-spin asymmetries 
show a signal stronger than for the proton and allow to perform a fully 
model-independent extraction of the $^4$He CFF $\mathcal{H}_A$. The extracted 
CFF is in a good agreement with the available models. This opens 
many new perspectives to study the nuclear structure within the GPD framework 
and pave the way for future more precise measurements at JLab 12~GeV to 
eventualy localize nuclear effects in the transverse plane.

>>>>

%conclusion
In summary, we present the first exclusive measurement of coherent DVCS 
off $^4$He using the CLAS spectrometer supplemented  
by a specially designed RTPC. This dataset represents a 
unique source as the first exclusive coherent nuclear DVCS measurement which 
can be used to directly constrain GPD models. The measured beam-spin asymmetries 
show a signal stronger than for the proton and allow to perform a fully 
model-independent extraction of the $^4$He CFF $\mathcal{H}_A$. The extracted 
CFF is in a good agreement with the available models. This opens 
many new perspectives to study the nuclear structure within the GPD framework 
and paves the way for future, more precise measurements at JLab 12~GeV to 
eventualy localize nuclear effects in the transverse plane.
